\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-13 manuscript.Rmd

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
#library(correlation)
library(ggcorrplot)
library(car) #Reversecoding
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
r_refs("references.bib")
```

>>>>

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(car) #Reversecoding
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
r_refs("references.bib")
```
